Assessing the Impact of Financial Assistances on Business and Income Outcomes: A Gender-Specific Analysis

### 2024-02-14 paper/paper.qmd
Update paper.qmd

---
title: "Assessing the Impact of Financial Assistances on Business and Income Outcomes: A Gender-Specific Analysis"
author: “Dinning Li Yiming Tang Yingqi Pang” 
date: “Feb 14 2024”
format: pdf
---

>>>>

---
title: "Assessing the Impact of Financial Assistances on Business and Income Outcomes: A Gender-Specific Analysis"
author: Dingning Li, Yiming Tang, Yingqi Pang 
date: “`r format(Sys.time(), '%d %B %Y')`”
format: pdf
---
